Notes for ISIPTA poster

### 2016-07-18 asce-paper.tex
Sec 4.1

We now consider a system of arbitrary layout,
consisting of components of $K$ types.
This system is observed until time $\tnow$,
leading to censored observations,
and we will explain in Section~\ref{sec:lambdawithcens}
how the scale parameter $\lambda_k$ for component type $k$
can be estimated in this situation.
%
Section~\ref{sec:sysrelwithsurvsign} describes then
how the system relibility function can be efficiently obtained using the survival signature.
%
For this, we need the posterior predictive distribution
of the number of components function at times $t > \tnow$,
which we will derive in Section~\ref{sec:postpred}.
%
Finally, in Section~\ref{sec:optimize} we describe how
the lower and upper bound for the system reliability function
are obtained when prior parameters $(\nkz,\ykz)$
vary in sets $\PkZ = [\nkzl,\nkzu] \times [\ykzl,\ykzu]$,
defining sets $\MkZ$ of prior distributions over $\lambda_k$,
as introduced in Section~\ref{sec:modforsurpr}.

@@

Consider observing a prototype system until $\tnow$,
where the system has $K$ different types of components,
and for each type $k$ there are $n_k$ components in the system.
Denoting the number of type $k$ components that have failed by $\tnow$ by $e_k$,
there are $n_k - e_k$ components still functioning at $\tnow$.
We denote the corresponding vector of observations by
\begin{linenomath*}
\begin{align}
\mbf{t}^k_{e_k;n_k} &= \big( \underbrace{t^k_1, \ldots, t^k_{e_k}}_{e_k \text{failure times}},
                             \underbrace{\tpnow, \ldots, \tpnow}_{n_k-e_k \text{censored obs.}} \big)\,,
\end{align}
\end{linenomath*}
where $t^+$ indicates a censored observation.

***change to general right-censoring? So $n_k-e_k \to c_k$, $e_k+c_k=n_k$,
introduce sets of observed and censored?

Posterior:
\begin{linenomath*}
\begin{align}
f_{\lambda_k\mid\ldots}(\lambda_k\mid\nkz,\ykz,\mbf{t}^k_{e_k;n_k})
 &\propto f_{\lambda_k}(\lambda_k)
          \big[ 1- F_k(\tnow\mid\lambda_k) \big]^{n_k-e_k}
          \prod_{i=1}^{e_k} f_k(t_i^k \mid \lambda_k) 
\end{align}
\end{linenomath*}
and so $\lambda_k\mid\nkz,\ykz,\mbf{t}^k_{e_k;n_k} \sim \ig(\nkn + 1, \nkn\ykn)$, where
\begin{linenomath*}
\begin{align}
\nkn + 1 &= \nkz + e_k + 1 \\
\nkn\ykn &= \nkz\ykz + (n_k-e_k) \tnow^\kappa + \sum_{i=1}^{e_k} (t_i^k)^\kappa
\end{align}
\end{linenomath*}
so the posterior expectation for $\lambda$ is
\begin{linenomath*}
\begin{align}
\E[\lambda_k\mid\nkn,\ykn] &= \ykn
                            = \frac{\nkz}{\nkz + e_k} \ykz +
                              \frac{e_k}{\nkz + e_k} \cdot \Big[\frac{n_k-e_k}{e_k} \tnow^\kappa + \frac{1}{e_k}\sum_{i=1}^{e_k} (t_i^k)^\kappa \Big]
\end{align}
\end{linenomath*}

@@

>>>>

We now consider a system of arbitrary layout,
consisting of components of $K$ types.
This system is observed until time $\tnow$,
leading to censored observation of lifetimes of components within the system,
and we will explain in Section~\ref{sec:lambdawithcens}
how the scale parameter $\lambda_k$ for component type $k$
can be estimated in this situation.
%
Section~\ref{sec:sysrelwithsurvsign} describes then
how the system reliability function can be efficiently obtained using the survival signature.
%
For this, we need the posterior predictive distribution
of the number of components function at times $t > \tnow$,
which we will derive in Section~\ref{sec:postpred}.
%
Finally, in Section~\ref{sec:optimize} we describe how
the lower and upper bound for the system reliability function
are obtained when prior parameters $(\nkz,\ykz)$
vary in sets $\PkZ = [\nkzl,\nkzu] \times [\ykzl,\ykzu]$,
defining sets $\MkZ$ of prior distributions over $\lambda_k$,
as introduced in Section~\ref{sec:modforsurpr}.

@@

Consider observing a prototype system until $\tnow$,
where the system has $K$ different types of components,
and for each type $k$ there are $n_k$ components in the system.
Denoting the number of type $k$ components that have failed by $\tnow$ by $e_k$,
there are $n_k - e_k$ components still functioning at $\tnow$.
We denote the corresponding vector of observations by
\begin{linenomath*}
\begin{align}
\mbf{t}^k_{e_k;n_k} &= \big( \underbrace{t^k_1, \ldots, t^k_{e_k}}_{e_k \text{failure times}},
                             \underbrace{\tpnow, \ldots, \tpnow}_{n_k-e_k \text{censored obs.}} \big)\,,
\end{align}
\end{linenomath*}
where $t^+$ indicates a right-censored observation.
%
%***change to general right-censoring? So $n_k-e_k \to c_k$, $e_k+c_k=n_k$,
%introduce sets of observed and censored?

According to Bayes' rule, multiplying the prior density and the likelihood
(which accounts for right-censored observations through the cdf terms)
gives a term proportional to the density of the posterior distribution for $\lambda_k$:
\begin{linenomath*}
\begin{align}
%f_{\lambda_k\mid\ldots}(\lambda_k\mid\nkz,\ykz,\mbf{t}^k_{e_k;n_k})
% &\propto f_{\lambda_k}(\lambda_k)
%          \big[ 1- F_k(\tnow\mid\lambda_k) \big]^{n_k-e_k}
%          \prod_{i=1}^{e_k} f_k(t_i^k \mid \lambda_k) 
f(\lambda_k\mid\nkz,\ykz,\mbf{t}^k_{e_k;n_k})
 &\propto f(\lambda_k)
          \big[ 1- F(\tnow\mid\lambda_k) \big]^{n_k-e_k}
          \prod_{i=1}^{e_k} f(t_i^k \mid \lambda_k) 
\end{align}
\end{linenomath*}
Conjugacy is preserved and we get 
$\lambda_k\mid\nkz,\ykz,\mbf{t}^k_{e_k;n_k} \sim \ig(\nkn + 1, \nkn\ykn)$, where
\begin{linenomath*}
\begin{align}
\nkn + 1 &= \nkz + e_k + 1 \\
\nkn\ykn &= \nkz\ykz + (n_k-e_k) (\tnow)^\beta + \sum_{i=1}^{e_k} (t_i^k)^\beta
\end{align}
\end{linenomath*}
are the updated parameters of the inverse gamma distribution.
%The posterior expectation for $\lambda_k$ is
%\begin{linenomath*}
%\begin{align}
%\E[\lambda_k\mid\nkn,\ykn] &= \ykn
%                            = \frac{\nkz}{\nkz + e_k} \ykz +
%                              \frac{e_k}{\nkz + e_k} \cdot \Big[\frac{n_k-e_k}{e_k} (\tnow)^\beta 
%                                                                    + \frac{1}{e_k} \sum_{i=1}^{e_k} (t_i^k)^\beta \Big]
%\end{align}
%\end{linenomath*}

@@

***from poster or similar
